Security on Networks

### 2013-05-16 paper/paper.tex
Adding references to the paper.

In this section, we present numerical results on the cost of anarchy and security difference as a function of the edge probability $p$ for various cost functions. Figures are shown for $n=10^8$.

\begin{figure}[H]
  \centering
  \includegraphics[width=6in]{cost_of_anarchy_q^2.png}
  \caption{Cost of Anarchy: $c(q) = q^2$}
  \label{cost_of_anarchy_q^2.fig}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=6in]{cost_of_anarchy_sqrt(1-q^2).png}
  \caption{Cost of Anarchy: $c(q) = \sqrt{1-q^2}$}
  \label{cost_of_anarchy_sqrt(1-q^2).fig}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=6in]{cost_of_anarchy_-q-log(1-q).png}
  \caption{Cost of Anarchy: $c(q) = -q - \log{1-q}$}
  \label{cost_of_anarchy_-q-log(1-q).fig}
\end{figure}

@@

  Solving for a mixed strategy Nash Equilibrium in this context is $PPAD$ complete.\footnote{\url{http://www.cs.berkeley.edu/~christos/papers/cacmDGP-2.pdf}} This implies that for all practical purposes, solving for a Nash Equilibrium is computationally intractable, although little is known about the actual complexity of $PPAD$ in relation to $P$ and $NP$.\footnote{\url{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=4031362}}

@@

In fact, there are provable bounds on how good our Monte Carlo results are for the approximation of $\tilde{P}_i$, given by Karp and Luby (1985) for the All Terminal problem (but can easily be extended to our problem):\footnote{See \url{http://www.sciencedirect.com/science/article/pii/0885064X85900214} for the full proof.}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{avg_prob_np05.png}
  \caption{Average Infection Rates with No Giant Component $np = 0.5 < 1$}
  \label{avg_prob_np05.fig}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{avg_prob_np5.png}
  \caption{Average Infection Rates with Giant Component $np = 5 > 1$}
  \label{avg_prob_np5.fig}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{network_effects_np5.png}
  \caption{Network Effect in a Giant Component ($np = 5$)}
  \label{network_effects_np5.fig}
\end{figure}

@@

Unfortunately, computing $\tilde{P}_i(A, q_{-i}, \Phi)$ in general for a graph which is not a tree is in $\# P$, which is as least as hard as $NP$. This makes computing $\tilde{P}$ computationally intractable.

@@

Showing the difficulty of the computation of $\tilde{P}_i$ in the static model is now as simple as showing a reduction of the Two Terminal Problem, since it is $\# P$ complete as shown by Ball (1980).\footnote{\url{http://onlinelibrary.wiley.com/doi/10.1002/net.3230100206/pdf}}

@@

\section{Fast FPTAS for Infection Probabilities}

@@

>>>>

In this section, we present numerical results on the cost of anarchy and security difference as a function of the edge probability $p$ for various cost functions. Figures \ref{cost_of_anarchy_q^2.fig}, \ref{cost_of_anarchy_sqrt(1-q^2).fig}, and \ref{cost_of_anarchy_-q-log(1-q).fig} show simulation results for various cost functions when $n=10^8$.

\begin{figure}[h!]
  \centering
  \includegraphics[width=6in]{cost_of_anarchy_q^2.png}
  \caption{Cost of Anarchy: $c(q) = q^2$}
  \label{cost_of_anarchy_q^2.fig}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=6in]{cost_of_anarchy_sqrt(1-q^2).png}
  \caption{Cost of Anarchy: $c(q) = \sqrt{1-q^2}$}
  \label{cost_of_anarchy_sqrt(1-q^2).fig}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=6in]{cost_of_anarchy_-q-log(1-q).png}
  \caption{Cost of Anarchy: $c(q) = -q - \log{1-q}$}
  \label{cost_of_anarchy_-q-log(1-q).fig}
\end{figure}

@@

Solving for a mixed strategy Nash Equilibrium in this context is $PPAD$ complete \cite{daskalakis08}. This implies that for all practical purposes, solving for a Nash Equilibrium is computationally intractable, although little is known about the actual complexity of $PPAD$ in relation to $P$ and $NP$ \cite{chen06}.

@@

In fact, there are provable bounds on how good our Monte Carlo results are for the approximation of $\tilde{P}_i$, given by Karp and Luby (1985) for the All Terminal problem (but can easily be extended to our problem). See \cite{karp-luby85} for the full proof.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=4in]{avg_prob_np05.png}
  \caption{Average Infection Rates with No Giant Component $np = 0.5 < 1$}
  \label{avg_prob_np05.fig}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=4in]{avg_prob_np5.png}
  \caption{Average Infection Rates with Giant Component $np = 5 > 1$}
  \label{avg_prob_np5.fig}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=4in]{network_effects_np5.png}
  \caption{Network Effect in a Giant Component ($np = 5$)}
  \label{network_effects_np5.fig}
\end{figure}

\section{Computational Intractibility Results}

Many of the critical parts required to simulate interesting scenarios of our model are NP hard. Unfortunately, this makes providing a broad range of simulation results difficult. In this section, we show a number of problems are NP hard, but also develop a polynomial time approximation scheme for computing infection probabilities.

@@

Computing $\tilde{P}_i(A, q_{-i}, \Phi)$ in general for a graph which is not a tree is in $\# P$, which is as least as hard as $NP$. This makes computing $\tilde{P}$ computationally intractable.

@@

Showing the difficulty of the computation of $\tilde{P}_i$ in the static model is now as simple as showing a reduction of the Two Terminal Problem, since it is $\# P$ complete as shown by Ball (1980) \cite{ball80}.

@@

Even the attacker's choice of target, on a general graph, cannot be computed with efficiency.

\begin{theorem}
  Computing the node to attack in order to have the highest expected number of infected nodes is NP hard.
\end{theorem}
\begin{proof}
  There is a direct bijection of this problem to the influence maximization problem, which has been shown to be NP hard by Kempe, Kleinberg, Tardos (2003) \cite{kempe-kleinberg-tardos03}.
\end{proof}

\subsection{Fast FPTAS for Infection Probabilities}

@@

\section{Conclusion}

In this paper, we presented a model of infection and characterized the cost of anarchy for different regimes. In addition, we ran simulations of the static and dynamic versions of the model to examined various properties of the resulting network.

We found a number of interesting problems related to our model were computationally intractable. For example, computing the probability of infection given a vector of protections for each node is NP-hard. However, we developed a polynomial time approximation scheme which can compute infection probabilities within an arbitrarily small range of their true values.

Our results show that purely selfish play on our model is worst (in comparison to the social optimal) when the network has an intermediate level of connectivity. Moreover, protection is ineffectual when the graph is disconnected, but has a large impact on slowing the spread of a disease when the graph is connected.·

This paper introduces a number of techniques for analyzing infection spread in networks. Our characterization of infection spread on Erdos Renyi graphs hopefully provides clearer insight into how infections spread in physical systems.

\newpage

\begin{thebibliography}{9}

  \bibitem{ball80}
    M. Ball.
    Complexity of Network Reliability Computations.
    \emph{Networks}, 1980.

  \bibitem{chen06}
    X. Chen and X. Deng.
    Settling the Complexity of Two-Player Nash Equilibrium.
    \emph{Foundations of Computer Science}, 2006.

  \bibitem{daskalakis08}
    C. Daskalakis, P. Goldberg, and C. Papadimitriou.
    The Complexity of Computing a Nash Equilibrium.
    \emph{SICOMP}, 2008.

  \bibitem{karp-luby85}
    R. Karp and M. Luby.
    Monte-Carlo Algorithms for the Planar Multiterminal Network Reliability Problem.
    \emph{Journal of Complexity}, 1985.

  \bibitem{kempe-kleinberg-tardos03}
    D. Kempe, J. Kleinberg, and E. Tardos.
    Maximizing the Spread of Inﬂuence Through a Social Network.
    \emph{SIGKDD}, 2003.

\end{thebibliography}
